---
title: "Regression Models Final Project"
output:
  pdf_document:
    fig_height: 7
    fig_width: 7
---
  
## Executive Summary  


## Exploratory Data Analysis  

```{r}
data(mtcars)
?mtcars

summary(mtcars$mpg[mtcars$am==0])
summary(mtcars$mpg[mtcars$am==1])
```   

## Regression Analysis  
First, we fit the full model as the following.  
```{r}
fullReg<-lm(mpg~.,data=mtcars)
summary(fullReg)
```  

```{r}
stepReg<-step(fullReg,k=log(nrow(mtcars)))
summary(stepReg)
```  

```{r}
boxplot(mpg~am,data = mtcars, ylab = "MPG",xlab = "Type (0=automatic, 1=manual)",main = "MPG by Transmission Type")
```  

```{r}
par(mfrow=c(2,2))
plot(stepReg)
```  

## Residual Analysis and Diagnostics  
Please refer to the **Appendix: Figures** section for the plots. According to the residual plots, we can verify the following underlying assumptions:  
1. The Residuals vs. Fitted plot shows no consistent pattern, supporting the accuracy of the independence assumption.  
2. The Normal Q-Q plot indicates that the residuals are normally distributed because the points lie closely to the line.  
3. The Scale-Location plot confirms the constant variance assumption, as the points are randomly distributed.  
4. The Residuals vs. Leverage argues that no outliers are present, as all values fall well within the 0.5 bands.  

As for the Dfbetas, the measure of how much an observation has effected the estimate of a regression coefficient, we get the following result:  
```{r}
sum((abs(dfbetas(amIntWtModel)))>1)
```  
Therefore, the above analyses meet all basic assumptions of linear regression and well answer the questions.  

## Appendix: Figures  
1. Boxplot of MPG vs. Transmission  
```{r}
boxplot(mpg ~ am, xlab="Transmission (0 = Automatic, 1 = Manual)", ylab="MPG",
        main="Boxplot of MPG vs. Transmission")
```  
2. Pair Graph of Motor Trend Car Road Tests  
```{r}
pairs(mtcars, panel=panel.smooth, main="Pair Graph of Motor Trend Car Road Tests")
```  
3. Scatter Plot of MPG vs. Weight by Transmission  
```{r}
ggplot(mtcars, aes(x=wt, y=mpg, group=am, color=am, height=3, width=3)) + geom_point() +  
scale_colour_discrete(labels=c("Automatic", "Manual")) + 
xlab("weight") + ggtitle("Scatter Plot of MPG vs. Weight by Transmission")
```  
4. Residual Plots
```{r}
par(mfrow = c(2, 2))
plot(amIntWtModel)
```  
