---
title: "Regression Models Final Project"
output:
  pdf_document:
    fig_height: 7
    fig_width: 7
---
  
## Executive Summary  
Through regression analysis, it is evident that manual transmissions yield a higher MPG than an automotic transmission. Holding all else constant, manual transmission receive approximately 2.94 MPG more than  automatic transmissions.

## Exploratory Data Analysis  

```{r}
data(mtcars)
?mtcars
```

Viewing the help on mtcars allows us to see the variables and how they are measured, particularly for transmission. If am = 0, the transmission is automoatic, 1 manual.

```{r}
summary(mtcars$mpg[mtcars$am==0])
summary(mtcars$mpg[mtcars$am==1])
```   

The mean of MPG for an automoatic transmission is 17.15, where the mean MPG for a manual transmission is 24.39. This is a very basic analysis, but shows at a cursory level that manual transmission will provide for a higher MPG.

## Regression Analysis  
In order to get more accurate and robust analysis of the effects of transmission type on MPG, we can conduct regression analysis.

The first model includes all variables provided.
```{r}
fullReg<-lm(mpg~.,data=mtcars)
summary(fullReg)
```  
This shows that a car with manual transmission will receive 2.52 MPG more than an automotic transmission, all else equal. This model is not very useful, though, because none of the values provided are statistically significant.

Therefore, we run a step regression, to narrow the number of variables in hope of making some significatn.
```{r}
stepReg<-step(fullReg,k=log(nrow(mtcars)))
summary(stepReg)
```  

In this case, wt, qsec, and am are included in the model and all are statistically significant. This model shows that a car with manual transmission will receive 2.94 MPG more than a car with automatic transmission, al else equal.

## Residual Analysis and Diagnostics 
```{r}
boxplot(mpg~am,data = mtcars, ylab = "MPG",xlab = "Type (0=automatic, 1=manual)",main = "MPG by Transmission Type")

```  

```{r}
par(mfrow = c(2, 2))
plot(amIntWtModel)
```  
